Robinson et al. 2020 Supplemental Information: Comparing the Radiocarbon and Tree-ring Records for the Upland US Southwest

### 2020-02-05 README.Rmd
color figs

## How to run in your broswer or download and run locally

The simplest way to explore the text, code and data is to click on [binder](https://mybinder.org/v2/gh/bocinsky/robinson2020/master?urlpath=rstudio) to open an instance of RStudio in your browser, which will have the compendium files ready to work with. Binder uses [rocker-project.org Docker] images to ensure a consistent and reproducible computational environment. These Docker images can also be used locally.

>>>>

## How to run in your browser or download and run locally

The simplest way to explore the text, code and data is to click on [binder](https://mybinder.org/v2/gh/bocinsky/robinson2020/master?urlpath=rstudio) to open an instance of RStudio in your browser, which will have the compendium files ready to work with. Binder uses (rocker-project.org)[rocker-project.org Docker] images to ensure a consistent and reproducible computational environment. These Docker images can also be used locally.

### 2020-02-05 analysis/paper/paper.Rmd
color figs

all_density %>%
  dplyr::bind_rows(vep_demography) %>%
  dplyr::mutate(
    Type = factor(Type,
      levels = c(
        "Radiocarbon Density",
        "Tree-ring Density",
        "Population"
      ),
      ordered = TRUE
    ),
    `Study Area` = factor(`Study Area`,
      levels = c(
        `Upland US Southwest` = "UUSW",
        `Central Mesa Verde` = "CMV",
        `Northern Rio Grande` = "NRG"
      )
    )
  ) %>%
  ggplot(aes(x = `Year AD`)) +
  geom_line(aes(
    y = Value,
    color = `Study Area`,
    size = `Study Area`
  )) +
  scale_color_manual(values = c(
    "UUSW" = "black",
    "CMV" = "gray50",
    "NRG" = "gray80"
  )) +
  scale_size_manual(values = c(
    "UUSW" = 1.25,
    "CMV" = 0.75,
    "NRG" = 0.75
  )) +
  # coord_cartesian(xlim = c(600,1600)) +
  xlab("Year AD") +
  scale_x_continuous(breaks = c(1, seq(200, 2000, 200))) +
  theme_minimal(18) +
  theme(
    legend.title = element_blank(),
    legend.justification = c(0, 1),
    legend.position = "bottom",
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(size = 10),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    plot.margin = unit(c(0.25, 0.5, 0.25, 0.25), "in")
  ) +
  facet_wrap("Type",
    nrow = 3,
    scales = "free_y"
  )
```

>>>>

all_density %>%
  dplyr::bind_rows(vep_demography) %>%
  dplyr::mutate(
    Type = factor(Type,
      levels = c(
        "Radiocarbon Density",
        "Tree-ring Density",
        "Population"
      ),
      ordered = TRUE
    ),
    `Study Area` = factor(`Study Area`,
      levels = c(
        `Upland US Southwest` = "UUSW",
        `Central Mesa Verde` = "CMV",
        `Northern Rio Grande` = "NRG"
      )
    )
  ) %>%
  ggplot(aes(x = `Year AD`)) +
  geom_line(aes(
    y = Value,
    color = `Study Area`,
    size = `Study Area`
  )) +
  scale_color_manual(values = c(
    "UUSW" = "#1b9e77",
    "CMV" = "#d95f02",
    "NRG" = "#7570b3"
  )) +
  scale_size_manual(values = c(
    "UUSW" = 1.25,
    "CMV" = 0.75,
    "NRG" = 0.75
  )) +
  # coord_cartesian(xlim = c(600,1600)) +
  xlab("Year AD") +
  scale_x_continuous(breaks = c(1, seq(200, 2000, 200))) +
  theme_minimal(18) +
  theme(
    legend.title = element_blank(),
    legend.justification = c(0, 1),
    legend.position = "bottom",
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(size = 10),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    plot.margin = unit(c(0.25, 0.5, 0.25, 0.25), "in")
  ) +
  facet_wrap("Type",
    nrow = 3,
    scales = "free_y"
  )
```
